---
title: "Descriptive Analysis"
output: html_notebook
---

Este es parte del proyecto de IDB (Inter-American Development Bank)
para mejorar los modelos de predicción de pobreza en Latinoamérica. 
En este caso en particular se analiza el caso de Costa Rica con datos
recopilados de variables sociodemográficas y de las viviendas de las personas. 

En este apartado se realiza un analisis descriptivo de la base de datos y las principales variables.

```{r, echo=F, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
```


## Se lee la base de datos
```{r}

datos <- read.csv('train.csv')

head(datos)

#plot(cars)
```


```{r}



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

